Discrete Quantum Theories and Computing

### 2019-04-07 dissertation.tex
dissertation.lyx "6.1 Summary" Updating...

Conventional quantum theory is defined over the continuum of complex
numbers, but each complex number can only be identified with unbounded
resources. To explore alternative versions of quantum theory incorporating
our limitation of distinguishability, two types of discrete quantum
theories have been described in this thesis: quantum theories and
computing over finite fields and quantum interval-valued probability
measures. Examining the computational and physical consequences of
such frameworks can yield new insights into not only the subtle properties
of conventional quantum theory but also the power and capacity of
quantum computing.

The theories over finite fields starting with unrestricted discrete
fields (modal theories), then advancing to a more reasonable framework
based on complexifiable discrete fields (discrete quantum theory I),
which lacks a notion of probability and supports unnaturally efficient
deterministic quantum algorithms. A still more plausible discrete
theory (discrete quantum theory II) is proposed, where conventional
quantum computing and conventional quantum theory emerge in a local
sense.

>>>>

Conventional quantum theory is defined over the continuum of complex
numbers, but we cannot distinguish two arbitrary complex numbers without
unbounded resources. To explore alternative versions of quantum theory
incorporating our limitation of distinguishability, two types of discrete
quantum theories have been described in this thesis: quantum theories
and computing over finite fields and quantum interval-valued probability
measures. Examining the computational and physical consequences of
such frameworks can yield new insights into not only the subtle properties
of conventional quantum theory but also the power and capacity of
quantum computing.

The theories over finite fields starting with unrestricted discrete
fields (modal theories), then advancing to a more reasonable framework
based on complexifiable discrete fields (discrete quantum theory I),
which lacks a notion of probability and supports unnaturally efficient
deterministic quantum algorithms. A still more plausible discrete
theory (discrete quantum theory II) is proposed, where conventional
quantum theory and computing emerge in a local sense. However, since
